Missing data: Current practice in football research and recommendations for reporting missingness

### 2020-09-02 paper/paper.Rmd
change wording in the intro

It is imperative that missing data (or lack thereof --Absence of
evidence is not evidence of absence) are reported. However, outside of
sports science, researchers seldom consider missing data [@Schafer2002].
Moreover, while there has been significant interest in modelling missing
data [@refs], the exploration and reporting of missing data have received
less attention [@Schafer2002]. This article aimed to: (1) estimate the proportion
of articles that report missing data in football research; (2) highlight
several bad missing data practices; and (3) provide recommendations for
exploring and reporting missingness.

>>>>

It is imperative that missing data, including lack thereof, are reported. However, outside of 
sports science, there is evidence that researchers seldom consider missing data [@Schafer2002]. 
While there has been significant interest in modelling missing
data [@refs], the exploration and reporting of missings have received
less attention [@Schafer2002]. This article aimed to: (1) estimate the proportion
of articles that report missing data in football research; (2) highlight
several improvable missing data practices; and (3) provide recommendations for
exploring and reporting missingness.
